Simulations of Ballot Polling Risk-Limiting Audits

### 2021-10-30 MultipleRoundSims/sections/05-results.tex
Added subsection on Selection-Ordered BRAVO
- plots
- figures, captions
- explanation

% \subsection{Selection-Ordered BRAVO}
% next_sample_size code is slow... tie simulations running still!

>>>>

\subsection{Selection-Ordered \BRAVO}
% next_sample_size code is slow... tie simulations running still!
For the SO \BRAVO simulations, our software estimated and used for each round
the minimum round size that would achieve a $90\%$ probability of stopping.
For the simulations with the announced outcome as the underlying
ballot distribution, for each round $j$ we computed the proportion of audits 
that stopped in round $j$ among those that had not stopped before round $j$.

\begin{figure}[H]
\includegraphics[width=\textwidth]{so_bravo_90perc_10^4/sprob_first_three.png}\caption{
For the first three rounds of the SO \BRAVO simulations, this plot shows the proportion of audits that stopped in the $j$th round
to all audits which had not yet stopped before the $j$th round.}
\label{fig:so_bravo_sprob}
\end{figure}

In Figure \ref{fig:so_bravo_sprob}, we again display proportions for only the first three rounds.
The proportions shown in Figure \ref{fig:so_bravo_sprob}, like those in \ref{fig:eor_bravo_sprob}, give an estimate
of the true probability of an SO \BRAVO audit stopping in the $j$th round,
given that it has not already stopped in a previous round. 
In \ref{fig:so_bravo_sprob}, we see that our round size predictions are relatively accurate,
all three rounds being near $90\%$.

Again, we will next consider the proportion of audits that stopped with an underlying tie over all five rounds.
This proportion, for a risk-limiting audit, should approach a value less than the risk limit, 
$0.1$, as more audits are performed.

\begin{figure}[H]
\includegraphics[width=\textwidth]{so_bravo_90perc_10^4/total_risk.png}
\caption{For each state margin, this plot shows
the proportion of SO \BRAVO audits with an underlying
tie that stopped in any of the five rounds.}
\label{fig:so_bravo_risk}
\end{figure}

In Figure~\ref{fig:so_bravo_risk} we show only the results for the $13$
states whose simulations with an underlying tie have finished running.
To estimate the minimum next round size that achieves a desired stopping probability,
the SO \BRAVO software generates the probability distribution ballot by ballot since
the stopping condition needs to be evaluated for each individual ballot drawn.
This means, when an underyling tie causes audits to quickly move on to larger rounds, 
the simulations are computationally expensive. 
Regardless, the claim that these simulations support, that SO \BRAVO is a Risk-Limiting Audit,
is a proven and well known result.
Notice in Figure~\ref{fig:so_bravo_risk},
that the risk of SO \BRAVO is much
nearer the risk limit than that of EoR \BRAVO.

%TODO SO and EoR macros
